Multi-task learning in Computer Vision

### 2020-03-31 5-Multitask.tex
Hard share done

\section{Hard parameter sharing}
A hard parameter sharing setting is one where the same convolutional weights in the intermediate layers solve multiple tasks, like in Figure 3.1.
Hard parameter sharing is the primary way of reducing total model size and inference time when solving multiple tasks simultaneously.
While sharing the weights can provide many benefits to the end model, as seen in the previous chapter, it comes at the cost of an increased number of tunable parameters when training the models.
As we have previously seen, Multi-task models introduce many new constant factors to the training process beyond the normal hyperparameters for learning rate, dropout rate, and others.
These include the hyperparameters for weighing the loss functions and determining the task sampling ratios, but also the expensive to evaluate which tasks should share representations and how much.

@@

Show how multiple heads can be combined to produce outputs for various tasks using different heads, show results from sharing all/some layers. \citep{visualPerson} \citep{selfDriving} \citep{healthyDrink}

>>>>

\section{Hard parameter sharing}
A hard parameter sharing setting is one where the same convolutional weights in the intermediate layers solve multiple tasks, like in Figure 3.1.
Hard parameter sharing is the primary way of reducing total model size and inference time when solving multiple tasks simultaneously.
While sharing the weights can provide many benefits to the end model, as seen in the previous chapter, it comes at the cost of an increased number of tunable parameters when training the models.
As we have previously seen, Multi-task models introduce many new constant factors to the training process beyond the normal hyperparameters for learning rate, dropout rate, and others.
These include the hyperparameters for weighing the loss functions and determining the task sampling ratios, but also the expensive to evaluate which tasks should share representations and how much should be shared.

@@

The two original features of interest were sugar and alcohol level in the drinks, and the other features were added as auxiliary training features to improve the performance \citep{healthyDrink}.
This auxiliary training can also be done by, for example, using ImageNet to keep the original classifier accurate on ImageNet while training on the new data set like in \citep{biologicalMultitask}; this way, the model won't be able to overfit on the new data so easily.
In the drink classification experiment, the auxiliary tasks were picked in a way that they might help in finding the correct features to solve the actual tasks \citep{healthyDrink}.
Adding auxiliary tasks is an interesting way of forcing features into the model that the developer thinks could be useful for the model to find, in that sense, they are hand-crafted features that get augmented in the model.
In practice, this means that if we are training a model to predict the steering angle, we might want to add an auxiliary task that predicts the lane markers to make it easier to learn these features.

A similar Multi-task model in \citep{visualPerson}, also partly visualized in Figure 3.1, solves 6 different tasks in a single model.
The tasks in that model are very different from one another, including person re-identification, pose estimation and image segmentation.
The interesting result in their search for related tasks is that while a pair of tasks don't work well together, they can work well when combined with other tasks.
For example, they found that just pairing the pose estimation head with other tasks significantly reduces its accuracy, but when all tasks use the single shared backbone, it does just as well as if trained in a single-task setting.
These results show that very different tasks can combine to a single model to provide a very significant reduction in model size while producing about as good or better accuracies.
